Global patterns of forest autotrophic carbon fluxes

### 2020-01-31 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

```{r setup, include = FALSE}
#knitr::opts_knit$set(root.dir = 'C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 92 | 42 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 256 | 80 |
| $ANPP_{woody-stem}$ | Woody stem growth component of $ANPP$ | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries | 264 | 96 |
| $ANPP_{foliage}$ | Foliage component of $ANPP$ | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Fine root component of $BNPP$ | fine roots | measurements combined one or more of the following: soil cores, minirhizotrons, turnover estimates,  root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | coarse and fine roots | partitioning of total soil respiration (e.g., through root exclusion), scaling of root gas exchange | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |

>>>>

```{r setup, include = FALSE}
# knitr::opts_knit$set(root.dir = 'C:/Users/gyrcbm/Dropbox/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 161 | 56 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 278 | 86 |
| $ANPP_{woody-stem}$ | Woody stem growth component of $ANPP$ | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries | 264 | 96 |
| $ANPP_{foliage}$ | Foliage component of $ANPP$ | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Fine root component of $BNPP$ | fine roots | measurements combined one or more of the following: soil cores, minirhizotrons, turnover estimates,  root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | coarse and fine roots | partitioning of total soil respiration (e.g., through root exclusion), scaling of root gas exchange | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |
